Lineage Analysis of CRISPR and shRNA Screens

### 2018-09-11 lineages_18Q3.Rmd
updated WIlcoxon tests

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180907.tsv", row.names = 1, sep = "\t", header = TRUE)
```

```{r, eval=FALSE, include=FALSE}
# Editing CCL DB
groupings <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
groupings <- unique(select(groupings, lineage_name, grouped_general_doid, group_general_lineage_name))

ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"

ccl_converter <- merge(ccl_converter, groupings, by = "lineage_name", all.x = TRUE)
```

@@

# Select columns
maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID", "Variant_Classification", "isDeleterious"))
colnames(maf_df)[colnames(maf_df) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
# Add Mutation_Status column
maf_df$Mutation_Status_Deleterious <- ifelse(maf_df$isDeleterious == TRUE, "Mutant", "Other")
maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
maf_df$Mutation_Status_DeleteriousMissense <- ifelse(maf_df$isDeleterious == TRUE | maf_df$Variant_Classification == "Missense", "Mutant", "Other")
maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Deleterious", "Mutation_Status_Nonsilent", "Mutation_Status_DeleteriousMissense")))

@@

```{r}
max(nchar(as.character(maf_raw$Tumor_Seq_Allele1)))
maf_raw %>% group_by(Variant_Type, isTCGAhotspot) %>% tally()

test <- filter(maf_raw, Hugo_Symbol == "KRAS")
test %>% group_by(isDeleterious) %>% tally()
```

@@

```{r}
crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
# write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
```

@@

@@

```{r, eval=TRUE}
crispr_signif <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif <- adj_signif(crispr_signif)
crispr_signif <- crispr_signif[order(crispr_signif$p),]
saveRDS(crispr_signif, "./data_munging/rds/crispr_signif_deleterious_gene.rds")

write.table(crispr_signif, file = "~/Desktop/crispr_signif_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif <- readRDS("./data_munging/rds/crispr_signif_deleterious_gene.rds")

knitr::kable(filter(crispr_signif, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_gene_plot <- ggplot(data = crispr_signif) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  coord_cartesian(ylim = c(0, 3500)) +
  scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_gene_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
```

@@

```{r, eval=TRUE}
crispr_signif_nonsilent <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_nonsilent <- adj_signif(crispr_signif_nonsilent)
crispr_signif_nonsilent <- crispr_signif_nonsilent[order(crispr_signif_nonsilent$p),]
saveRDS(crispr_signif_nonsilent, "./data_munging/rds/crispr_signif_nonsilent_gene.rds")

write.table(crispr_signif_nonsilent, file = "~/Desktop/crispr_signif_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r, eval=TRUE}
crispr_signif_delmis <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_delmis <- adj_signif(crispr_signif_delmis)
crispr_signif_delmis <- crispr_signif_delmis[order(crispr_signif_delmis$p),]
saveRDS(crispr_signif_delmis, "./data_munging/rds/crispr_signif_deleteriousmissense_gene.rds")

write.table(crispr_signif_delmis, file = "~/Desktop/crispr_signif_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r, eval=TRUE}
crispr_signif_lineage <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_lineage <- adj_signif(crispr_signif_lineage)
crispr_signif_lineage <- crispr_signif_lineage[order(crispr_signif_lineage$p),]
saveRDS(crispr_signif_lineage, "./data_munging/rds/crispr_signif_deleterious_lineage.rds")

write.table(crispr_signif_lineage, file = "~/Desktop/crispr_signif_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_lineage <- readRDS("./data_munging/rds/crispr_signif_deleterious_lineage.rds")

knitr::kable(filter(crispr_signif_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_lineage_plot <- ggplot(data = crispr_signif_lineage) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  # coord_cartesian(ylim = c(0, 3500)) +
  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_lineage_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
```

@@

```{r, eval=TRUE}
crispr_signif_nonsilent_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_nonsilent_lineage <- adj_signif(crispr_signif_nonsilent_lineage)
crispr_signif_nonsilent_lineage <- crispr_signif_nonsilent_lineage[order(crispr_signif_nonsilent_lineage$p),]
saveRDS(crispr_signif_nonsilent_lineage, "./data_munging/rds/crispr_signif_nonsilent_lineage.rds")

write.table(crispr_signif_nonsilent_lineage, file = "~/Desktop/crispr_signif_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r, eval=TRUE}
crispr_signif_delmis_lineage <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_delmis_lineage <- adj_signif(crispr_signif_delmis_lineage)
crispr_signif_delmis_lineage <- crispr_signif_delmis_lineage[order(crispr_signif_delmis_lineage$p),]
saveRDS(crispr_signif_delmis_lineage, "./data_munging/rds/crispr_signif_deleteriousmissense_lineage.rds")

write.table(crispr_signif_delmis_lineage, file = "~/Desktop/crispr_signif_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=TRUE}
crispr_signif_tissue <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_tissue <- adj_signif(crispr_signif_tissue)
crispr_signif_tissue <- crispr_signif_tissue[order(crispr_signif_tissue$p),]
saveRDS(crispr_signif_tissue, "./data_munging/rds/crispr_signif_deleterious_tissue.rds")

write.table(crispr_signif_tissue, file = "~/Desktop/crispr_signif_deleterious_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_tissue <- readRDS("./data_munging/rds/crispr_signif_deleterious_tissue.rds")

knitr::kable(filter(crispr_signif_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_tissue_plot <- ggplot(data = crispr_signif_tissue) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  # scale_y_continuous(breaks = seq(0, 50000, by = 5000), labels = formatC(seq(0, 50000, by = 5000), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_tissue_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_tissue_plot, width = 8, height = 4, device = "pdf")
```

@@

```{r, eval=TRUE}
crispr_signif_nonsilent_tissue <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_nonsilent_tissue <- adj_signif(crispr_signif_nonsilent_tissue)
crispr_signif_nonsilent_tissue <- crispr_signif_nonsilent_tissue[order(crispr_signif_nonsilent_tissue$p),]
saveRDS(crispr_signif_nonsilent_tissue, "./data_munging/rds/crispr_signif_nonsilent_tissue.rds")

write.table(crispr_signif_nonsilent_tissue, file = "~/Desktop/crispr_signif_nonsilent_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r, eval=TRUE}
crispr_signif_delmis_tissue <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_delmis_tissue <- adj_signif(crispr_signif_delmis_tissue)
crispr_signif_delmis_tissue <- crispr_signif_delmis_tissue[order(crispr_signif_delmis_tissue$p),]
saveRDS(crispr_signif_delmis_tissue, "./data_munging/rds/crispr_signif_deleteriousmissense_tissue.rds")

write.table(crispr_signif_delmis_tissue, file = "~/Desktop/crispr_signif_deleteriousmissense_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r fig.height=12, fig.width=12, include=FALSE}
makeCRISPRgrob("KRAS")
```

@@

```{r fig.height=12, fig.width=12, include=FALSE}
makeCRISPRlinplot("KRAS")
```

@@

```{r fig.height=12, fig.width=12, include=FALSE}
makeCRISPRtissueplot("KRAS")
```

@@

```{r}
maf_df_filt <- filter(maf_df, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
maf_summ_filt <- maf_df_filt %>% group_by(Mutation_Status) %>% tally()
maf_summ_filt$Percent <- format(round(maf_summ_filt$n / sum(maf_summ_filt$n) * 100, 4), nsmall = 2)
maf_summ_filt$Percent <- as.numeric(as.character(maf_summ_filt$Percent))
```

>>>>

This comprehensive cancer cell line information curated by Daniel Charytonowicz.
```{r}
ccl_converter <- read.delim("./data_munging/cell_line_database_v1_20180911.tsv", row.names = 1, sep = "\t", header = TRUE)
```

```{r, eval=FALSE, include=FALSE}
# Editing CCL DB
# groupings <- read.delim("./data_munging/cell_line_database_completed_extra_grouped_doids_FINAL.csv", sep = "\t", header = TRUE)
# groupings <- unique(select(groupings, lineage_name, grouped_general_doid, group_general_lineage_name))
# ccl_converter <- read.delim("./data_munging/cell_line_database_FINAL_MASTER.tsv", sep = "\t", row.names = 1, header = TRUE)
# colnames(ccl_converter)[colnames(ccl_converter) == "ccle_cell_line_name"] <- "CCLE_Name"
# colnames(ccl_converter)[colnames(ccl_converter) == "broad_id"] <- "Broad_ID"
# ccl_converter <- merge(ccl_converter, groupings, by = "lineage_name", all.x = TRUE)

# Testing completeness of grouped lineage names
unique(ccl_converter$group_general_lineage_name)
test <- filter(ccl_converter, is.na(group_general_lineage_name))
unique(test$lineage_name)
test2 <- filter(ccl_converter, is.na(grouped_general_doid))
```

@@

# Select columns
maf_df <- subset(maf_raw, select = c("Hugo_Symbol", "Tumor_Sample_Barcode", "Broad_ID", "Variant_Classification", "isDeleterious", "Reference_Allele"))
colnames(maf_df)[colnames(maf_df) == "Tumor_Sample_Barcode"] <- "CCLE_Name"
maf_df$Var_Length <- nchar(as.character(maf_df$Reference_Allele))

# Add Mutation_Status column
maf_df$Mutation_Status_Deleterious <- ifelse(maf_df$isDeleterious == TRUE, "Mutant", "Other")
maf_df$Mutation_Status_Nonsilent <- ifelse(maf_df$Variant_Classification == "Silent", "Other", "Mutant")
maf_df$Mutation_Status_DeleteriousMissense <- ifelse(maf_df$isDeleterious == TRUE | maf_df$Variant_Classification == "Missense_Mutation", "Mutant", "Other")
maf_df <- unique(subset(maf_df, select = c("Hugo_Symbol", "CCLE_Name", "Broad_ID", "Mutation_Status_Deleterious", "Mutation_Status_Nonsilent", "Mutation_Status_DeleteriousMissense", "Var_Length")))

@@

```{r}
max(nchar(as.character(maf_raw$Reference_Allele)))
maf_raw %>% group_by(Variant_Type, isTCGAhotspot) %>% tally()

test <- filter(maf_df, Hugo_Symbol == "KRAS")
test %>% group_by(isDeleterious) %>% tally()
```

@@

```{r}
crispr_data <- readRDS("./../crispr_lineages_giant_files/crispr_data_18Q3.rds")
# crispr_ccl <- data.frame("Broad_ID" = crispr_data$Broad_ID)
# write.table(crispr_data, file = "~/Desktop/crispr_data.tsv", quote = FALSE, sep = "\t")
```

@@

Filter for point mutations:
```{r}
crispr_data_ptmuts <- filter(crispr_data, Var_Length == 1)
test_ptmuts <- filter(crispr_data_ptmuts, is.na(group_general_lineage_name))
```

@@

```{r, eval=FALSE}
crispr_signif_del <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_del <- adj_signif(crispr_signif_del)
crispr_signif_del <- crispr_signif_del[order(crispr_signif_del$p),]
saveRDS(crispr_signif_del, "./data_munging/rds/crispr_signif_deleterious_gene.rds")

# write.table(crispr_signif_del, file = "~/Desktop/crispr_signif_deleterious_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_del <- readRDS("./data_munging/rds/crispr_signif_deleterious_gene.rds")

knitr::kable(filter(crispr_signif_del, p < 0.05)[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_gene_plot <- ggplot(data = crispr_signif_del) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_gene_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
```

@@

```{r, eval=FALSE}
crispr_signif_nonsilent <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_nonsilent <- adj_signif(crispr_signif_nonsilent)
crispr_signif_nonsilent <- crispr_signif_nonsilent[order(crispr_signif_nonsilent$p),]
saveRDS(crispr_signif_nonsilent, "./data_munging/rds/crispr_signif_nonsilent_gene.rds")

# write.table(crispr_signif_nonsilent, file = "~/Desktop/crispr_signif_nonsilent_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r, eval=FALSE}
crispr_signif_delmis <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_delmis <- adj_signif(crispr_signif_delmis)
crispr_signif_delmis <- crispr_signif_delmis[order(crispr_signif_delmis$p),]
saveRDS(crispr_signif_delmis, "./data_munging/rds/crispr_signif_deleteriousmissense_gene.rds")

# write.table(crispr_signif_delmis, file = "~/Desktop/crispr_signif_deleteriousmissense_gene.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r, eval=FALSE}
crispr_signif_del_lineage <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_del_lineage <- adj_signif(crispr_signif_del_lineage)
crispr_signif_del_lineage <- crispr_signif_del_lineage[order(crispr_signif_del_lineage$p),]
saveRDS(crispr_signif_del_lineage, "./data_munging/rds/crispr_signif_deleterious_lineage.rds")

# write.table(crispr_signif_del_lineage, file = "~/Desktop/crispr_signif_deleterious_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_del_lineage <- readRDS("./data_munging/rds/crispr_signif_deleterious_lineage.rds")

knitr::kable(filter(crispr_signif_del_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by lineage, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_lineage_plot <- ggplot(data = crispr_signif_del_lineage) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  # coord_cartesian(ylim = c(0, 3500)) +
  # scale_y_continuous(breaks = seq(0, 3500, by = 500), labels = formatC(seq(0, 3500, by = 500), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_lineage_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes.pdf", plot = wilcox_gene_plot, width = 8, height = 4, device = "pdf")
```

@@

```{r, eval=FALSE}
crispr_signif_nonsilent_lineage <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_nonsilent_lineage <- adj_signif(crispr_signif_nonsilent_lineage)
crispr_signif_nonsilent_lineage <- crispr_signif_nonsilent_lineage[order(crispr_signif_nonsilent_lineage$p),]
saveRDS(crispr_signif_nonsilent_lineage, "./data_munging/rds/crispr_signif_nonsilent_lineage.rds")

# write.table(crispr_signif_nonsilent_lineage, file = "~/Desktop/crispr_signif_nonsilent_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r, eval=FALSE}
crispr_signif_delmis_lineage <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "group_general_lineage_name"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_delmis_lineage <- adj_signif(crispr_signif_delmis_lineage)
crispr_signif_delmis_lineage <- crispr_signif_delmis_lineage[order(crispr_signif_delmis_lineage$p),]
saveRDS(crispr_signif_delmis_lineage, "./data_munging/rds/crispr_signif_deleteriousmissense_lineage.rds")

# write.table(crispr_signif_delmis_lineage, file = "~/Desktop/crispr_signif_deleteriousmissense_lineage.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

knitr::kable(filter(crispr_signif_delmis_lineage, p < 0.05)[, c("Hugo_Symbol", "group_general_lineage_name", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious and missense mutant and other cell lines, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
crispr_signif_del_tissue <- compare_means(Score ~ Mutation_Status_Deleterious, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_del_tissue <- adj_signif(crispr_signif_del_tissue)
crispr_signif_del_tissue <- crispr_signif_del_tissue[order(crispr_signif_del_tissue$p),]
saveRDS(crispr_signif_del_tissue, "./data_munging/rds/crispr_signif_deleterious_tissue.rds")

# write.table(crispr_signif_del_tissue, file = "~/Desktop/crispr_signif_deleterious_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

```{r}
crispr_signif_del_tissue <- readRDS("./data_munging/rds/crispr_signif_deleterious_tissue.rds")

knitr::kable(filter(crispr_signif_del_tissue, p < 0.05)[, c("Hugo_Symbol", "primary_tissue", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results comparing deleterious mutant and other cell lines by tissue, p < 0.05 (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% footnote(general = "Wilcoxon test Benjamini-Hochberg-corrected p-values:\n*: p <= 0.05\n**: p <= 0.01\n***: p <= 0.001\n****: p <= 0.0001") %>% scroll_box(width = "900px", height = "450px")
```

```{r fig.height=4, fig.width=8}
wilcox_tissue_plot <- ggplot(data = crispr_signif_del_tissue) +
  geom_histogram(aes(x = p, fill = "chartreuse4"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  geom_histogram(aes(x = p.adj, fill = "darkslategray3"), breaks = seq(0, 1, by = 0.025), color = "black", alpha = 0.7) +
  scale_x_continuous(breaks = seq(0, 1, by = 0.05), labels = seq(0, 1, by = 0.05)) +
  # scale_y_continuous(breaks = seq(0, 50000, by = 5000), labels = formatC(seq(0, 50000, by = 5000), format = "d")) +
  scale_fill_manual(name = "P-values", values = c("chartreuse4" = "chartreuse4", "darkslategray3" = "darkslategray3"), labels = c("Unadjusted", "BH-adjusted")) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = c(0.1, 0.85)) +
  labs(x = "BH-adjusted p-values", y = "Frequency")
wilcox_tissue_plot
# ggsave(filename = "./plots_18Q3/crispr/pvals_genes_tissues.pdf", plot = wilcox_tissue_plot, width = 8, height = 4, device = "pdf")
```

@@

```{r, eval=FALSE}
crispr_signif_nonsilent_tissue <- compare_means(Score ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_nonsilent_tissue <- adj_signif(crispr_signif_nonsilent_tissue)
crispr_signif_nonsilent_tissue <- crispr_signif_nonsilent_tissue[order(crispr_signif_nonsilent_tissue$p),]
saveRDS(crispr_signif_nonsilent_tissue, "./data_munging/rds/crispr_signif_nonsilent_tissue.rds")

# write.table(crispr_signif_nonsilent_tissue, file = "~/Desktop/crispr_signif_nonsilent_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r, eval=FALSE}
crispr_signif_delmis_tissue <- compare_means(Score ~ Mutation_Status_DeleteriousMissense, group.by = c("Hugo_Symbol", "primary_tissue"), data = crispr_data_ptmuts, method = "wilcox.test", p.adjust.method = "BH")
crispr_signif_delmis_tissue <- adj_signif(crispr_signif_delmis_tissue)
crispr_signif_delmis_tissue <- crispr_signif_delmis_tissue[order(crispr_signif_delmis_tissue$p),]
saveRDS(crispr_signif_delmis_tissue, "./data_munging/rds/crispr_signif_deleteriousmissense_tissue.rds")

# write.table(crispr_signif_delmis_tissue, file = "~/Desktop/crispr_signif_deleteriousmissense_tissue.csv", quote = FALSE, sep = ",", row.names = FALSE)
```

@@

```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
makeCRISPRgrob("KRAS")
```

@@

```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
makeCRISPRlinplot("KRAS")
```

@@

```{r fig.height=12, fig.width=12, include=FALSE, eval=FALSE}
makeCRISPRtissueplot("KRAS")
```

@@

```{r}
maf_df_filt <- filter(maf_df, Hugo_Symbol %in% unique(crispr_data$Hugo_Symbol))
# maf_summ_filt <- maf_df_filt %>% group_by(Mutation_Status) %>% tally()
# maf_summ_filt$Percent <- format(round(maf_summ_filt$n / sum(maf_summ_filt$n) * 100, 4), nsmall = 2)
# maf_summ_filt$Percent <- as.numeric(as.character(maf_summ_filt$Percent))
```
